\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{xr}
\externaldocument{hrf}

% Referee comment box
\newmdenv[
  linecolor=gray!50,
  backgroundcolor=gray!8,
  innerleftmargin=10pt,
  innerrightmargin=10pt,
  innertopmargin=8pt,
  innerbottommargin=8pt,
  skipabove=10pt,
  skipbelow=4pt
]{refbox}

\newcommand{\comment}[1]{\begin{refbox}\textit{#1}\end{refbox}}
\newcommand{\response}{\medskip\noindent\textbf{Response.}\ }
\newcommand{\hrf}{\textsc{hrf}}
\newcommand{\rf}{\textsc{rf}}

\title{Response to Referee Report\\[6pt]
  \large ``Hedged Random Forest''\\
  \normalsize Journal of Financial Econometrics --- JFEC-2025-167}
\author{E.\ Beck \and D.\ Kozbur \and M.\ Wolf}
\date{}

\begin{document}
\maketitle
\thispagestyle{empty}

We thank the referee for the careful reading and constructive suggestions.
The report has led to meaningful improvements in the paper.
Below we address each point in turn.
All section, equation, and table references are to the revised manuscript.

% ============================================================
\section*{Main Comments}
% ============================================================

% -----------------------------------------------------------
\subsection*{Comment 1}
% -----------------------------------------------------------

\comment{Why not carry out estimation on a second sample using standard OLS
with constraints on the weights, which is also a standard approach
(Timmermann, 2006)?  Ridge would require to tune a parameter, but this
could be done by AIC, though ad hoc.  Of course, this is a different
estimator, but a reader may want to understand the distinction and whether
one approach is better than the other.}

\response
We have implemented a second-sample benchmark in the spirit of
\citet{timmermann:2006}.
The approach splits the training data in half: the random forest is trained
on the first half, and the tree-level weights are estimated on the second
half (which the trees have never seen).

A pure OLS estimator on the second sample is not viable here because the
number of trees ($B = 500$) far exceeds the second-sample size ($n/2$),
making the system severely underdetermined.
Ridge regression with a sum-to-one constraint handles the high-dimensional
regime gracefully; we select the penalty parameter $\lambda$ by AIC using
the analytical hat-matrix trace for the equality-constrained problem.
We refer to this estimator as \textit{Ridge\textsubscript{2nd}}.

% TODO: add forward reference to new table/figure once results are finalised.
The empirical results are reported in [TABLE/FIGURE REF].
[RESULTS DISCUSSION PENDING --- fill in once final experiment is complete.]

% -----------------------------------------------------------
\subsection*{Comment 2}
% -----------------------------------------------------------

\comment{Why not carrying out estimation on the same sample using a ridge
regression?  Again, helping the reader see the distinction and the merits
of one method over the other could be useful.}

\response
We have added a same-sample ridge regression benchmark (Ridge).
As with the second-sample variant, we impose the sum-to-one constraint and
select $\lambda$ by AIC.
Because the constraint is an equality, the standard ridge hat matrix must be
corrected; we derive the exact effective degrees of freedom analytically via
the economy SVD of the tree-prediction matrix.

% TODO: add forward reference to new table/figure once results are finalised.
The results are reported alongside the other benchmarks in [TABLE/FIGURE
REF].
[RESULTS DISCUSSION PENDING --- fill in once final experiment is complete.]

% -----------------------------------------------------------
\subsection*{Comment 3}
% -----------------------------------------------------------

\comment{Why not focusing on variance minimisation, as for a minimum variance
portfolio?  Once the weights are derived this way and fixed, the bias, which
is a constant, could be removed in a second step, when forecasting.}

\response
We have implemented the minimum variance (MV) portfolio as an additional
benchmark.
The weights are obtained by minimising $\mathbf{w}^{\top}\widehat{\boldsymbol{\Sigma}}\mathbf{w}$
subject to $\mathbf{1}^{\top}\mathbf{w}=1$ and the leverage constraint
$\|\mathbf{w}\|_1\leq\kappa$, with $\kappa\in\{1,2\}$.
The systematic bias of the combined predictor,
$\hat{b} = \mathbf{w}^{\top}\bar{\mathbf{r}}$ where $\bar{\mathbf{r}}$
denotes the vector of mean training residuals, is then subtracted from each
test prediction.
We implement both the sample and the shrunk (Ledoit--Wolf NLS) covariance
variants, mirroring the \hrf\ design.

% TODO: add forward reference to new table/figure once results are finalised.
The results are reported in [TABLE/FIGURE REF] and discussed in
Comment~4 below.

% -----------------------------------------------------------
\subsection*{Comment 4}
% -----------------------------------------------------------

\comment{Individual trees tend to have low bias but high variance, so the
variance component may dominate in practice.  This justifies the use of the
sample mean for the estimator of the bias of the individual trees, i.e.\ they
are small numbers close to zero dominated by the variance.  Would the
estimator perform the same or perhaps better if we just used a minimum
variance portfolio approach and forgot about the bias?}

\response
The empirical results for the MV benchmark described in Comment~3 provide a
direct answer.
Across all datasets and sample sizes, the performance of
MV (shrunk, $\kappa=2$) and \hrf\ (shrunk, $\kappa=2$) is virtually
identical, confirming the referee's intuition that the bias term in the joint
objective contributes little in practice.
Individual tree biases are indeed small relative to the variance, so the
\hrf\ objective is effectively dominated by the variance component.

This finding is informative in two directions.
First, it validates the \hrf\ design: the method works well even though the
bias estimation step is noisy, because the variance component is what matters.
Second, it provides a useful robustness check for practitioners: a
pure variance-minimisation approach with a post-hoc bias correction is
equally effective and even simpler to implement.

% TODO: reference the specific numbers from the final table.

% -----------------------------------------------------------
\subsection*{Comment 5}
% -----------------------------------------------------------

\comment{What is very interesting about negative weights is that they should
work better in situations where the trees are correlated.  From portfolio
optimisation theory we know that the weights will be all positive if the
correlations of the trees were small.  However, negative weights become more
likely as correlations increase.  Hence, the authors' method becomes even
more important and relevant when features are correlated, making tree
decorrelation more difficult.  I think remarking on the properties of
portfolio weights (especially in light of Point 4) as a function of
correlations would be relevant.}

\response
We thank the referee for this insightful observation, which we now make
explicit in the paper (Section~\ref*{sec:neg-weights}).

The connection follows directly from classical results in portfolio theory.
When the trees are mutually uncorrelated, the minimum-variance weights are
all positive: there is no benefit to short positions because each tree
contributes independent variance reduction.
As pairwise tree correlations increase, the optimal portfolio can reduce
variance further by going short on the most ``redundant'' trees, using
their predictions to cancel noise shared with other trees.
The leverage constraint $\|\mathbf{w}\|_1 \leq \kappa$ controls the degree
to which this is permitted: $\kappa = 1$ restricts weights to be non-negative
(no short-selling), while $\kappa = 2$ allows negative weights.

In the random forest setting this has a natural interpretation.
Trees are constructed to be decorrelated via feature subsampling
(the \texttt{mtry} parameter), but this decorrelation is imperfect when
the input features are themselves highly correlated.
In such datasets the trees remain substantially correlated, and the gains
from $\kappa = 2$ over $\kappa = 1$ are expected to be largest.
Conversely, when features are nearly independent, trees are already
well-decorrelated, $\kappa = 1$ suffices, and the additional flexibility of
$\kappa = 2$ adds little.
This provides a characterisation of when \hrf\ with negative weights is most
valuable, and it is consistent with the empirical patterns we observe across
the benchmark datasets.
The corresponding passage has been added to Section~\ref*{sec:neg-weights}
of the revised manuscript.

% ============================================================
\section*{Additional Comments}
% ============================================================

% -----------------------------------------------------------
\subsection*{Additional Comment 1}
% -----------------------------------------------------------

\comment{It would be interesting to know whether one can learn something about
the methodology and the HRF estimator from the individual characteristics of
the datasets (e.g., variable correlations, fat-tailed data etc.).  For
instance, are there certain data features that systematically relate to larger
performance gains?}

\response
% TODO: Run dataset characteristics analysis and summarise findings here.
[RESPONSE PENDING]

% -----------------------------------------------------------
\subsection*{Additional Comment 2}
% -----------------------------------------------------------

\comment{Many readers will naturally associate the leverage constraint with a
Lasso-type penalty and therefore expect a sparse solution, i.e.\ that only a
small number of trees receive nonzero weights.  However, the additional
portfolio equality constraint (i.e., the requirement that the weights sum to
one) changes the geometry of the optimisation problem, and often leads instead
to a dense weighting scheme.  It might be helpful to include a short remark
about this.}

\response
We have added Remark~\ref*{rem:dense} to Section~\ref*{sec:hrf} of the
revised manuscript.

The key distinction is geometric.
An L1 penalty alone (without any equality constraint) encourages sparsity
because the corners of the L1 ball align with coordinate axes: the
penalised objective is minimised at a vertex, where all but a few weights
are zero.
The sum-to-one equality constraint $\mathbf{1}^{\top}\mathbf{w} = 1$,
however, restricts the feasible region to a hyperplane that generically
passes through the interior of the L1 ball rather than through its
sparse vertices.
The constrained solution therefore lies on the hyperplane, which is a
full-dimensional affine subspace; there is no geometric pressure towards
the coordinate-axis corners, and the solution is typically dense.

Intuitively, the difference between Lasso and \hrf\ is analogous to the
difference between asset selection (Lasso finds a sparse subset of trees
with non-zero weight) and portfolio construction (\hrf\ assigns a weight to
every tree, possibly including short positions, to minimise prediction
error).

% -----------------------------------------------------------
\subsection*{Additional Comment 3}
% -----------------------------------------------------------

\comment{In section 3, the authors define their specific implementation of the
estimator: shrunk covariance matrix and a leverage constraint equal to 2.
Later in the paper, they compare results with a leverage constraint equal to
one and also compare to the estimator that uses the standard sample covariance
matrix.  A number of different intuitive notations are used to define these.
It would be ideal if this notation or some similar version could be used
everywhere.  Using shrinkage/sample and $\kappa$ (the leverage constraint)
equal to 1 or 2, everywhere is a possible solution.}

\response
We thank the referee for this suggestion.
We have unified the notation throughout the paper along the lines proposed.
Each variant of the estimator is now identified by two labels: the covariance
estimator used (``shrinkage'' for the Ledoit--Wolf NLS estimator,
``sample'' for the plain sample covariance) and the leverage parameter
$\kappa \in \{1, 2\}$.
For example, the main \hrf\ specification discussed in Section~3 is now
consistently referred to as \hrf\ (shrinkage, $\kappa = 2$), and this
labelling is used uniformly in the text, all tables, and the appendix,
including the notation tables in Section~\ref*{sec:results} and the appendix.

% ============================================================
\bibliographystyle{plainnat}
\bibliography{wolf}
% ============================================================

\end{document}
